old snippets

### 2024-12-18 manuscript/masked_manuscript.qmd
anonymized links in masked manuscript

We have reported how we determined our sample size, all data exclusions, and all measures in the study.
The preregistration, analysis code, and study materials, can be found on the article's GitHub repository (<https://github.com/stefanvermeent/liss_ef_2024>).
The newly collected data will be available for other researchers in the LISS data archive, after signing a data use agreement (https://lissdata.nl).
For more information on the LISS variables used, see the article's GitHub repository (<https://github.com/stefanvermeent/liss_ef_2024>).
Our study complies with Level 2 of the Transparency and Openness Promotion (TOP) guidelines.

>>>>

We have reported how we determined our sample size, all data exclusions, and all measures in the study.
The preregistration, analysis code, and study materials, can be found on the article's GitHub repository (<https://anonymous.4open.science/w/liss_ef_anon/>).
The newly collected data will be available for other researchers in the LISS data archive, after signing a data use agreement (https://lissdata.nl).
For more information on the LISS variables used, see the article's GitHub repository (<https://anonymous.4open.science/w/liss_ef_anon/>).
Our study complies with Level 2 of the Transparency and Openness Promotion (TOP) guidelines.
